\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{float}
\usepackage{pdflscape}

\geometry{margin=1in}
\setlength{\parindent}{0pt}

% Define colors
\definecolor{primary}{RGB}{30, 58, 138}
\definecolor{secondary}{RGB}{79, 70, 229}
\definecolor{success}{RGB}{16, 185, 129}
\definecolor{warning}{RGB}{245, 158, 11}
\definecolor{danger}{RGB}{239, 68, 68}

% Header and footer
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\textbf{\textcolor{primary}{ Tender Evaluation Report }}}
\fancyhead[R]{\thepage}
\fancyfoot[C]{\textcolor{gray}{AI-Powered Tender Evaluation Report}}

\title{\textbf{\textcolor{primary}{ Tender Evaluation Report }}}
\date{ 2025-10-07 }
\author{AI Tender Evaluation System}

\begin{document}

\maketitle

\section*{Executive Summary}
This report presents the evaluation results of tender proposals against the organization's requirements. The evaluation was performed using AI-powered analysis including semantic similarity matching and LLM-based reasoning.

\section*{Organization Requirements}

\begin{itemize}
    \item TENDER DOCUMENT
Project: Software Development Services
Requirements:
1. Minimum 5 years experience
2. Valid business license
3. Technical specifications compliance
4. Project timeline and...
\end{itemize}


\section*{Evaluation Results Summary}
\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{|l|X|l|}
\hline
\textbf{Metric} & \textbf{Value} \\
\hline
Total Applicants Evaluated & 2 \\
Average Compliance Score & 81.0 \\
Top Applicant Score & 83 \\
\hline
\end{tabularx}
\caption{Evaluation Summary}
\end{table}

\section*{Applicant Comparison Table}

\begin{longtable}{|c|p{3cm}|c|c|p{4cm}|p{3cm}|}
\hline
\textbf{Rank} & \textbf{Applicant} & \textbf{Similarity} & \textbf{Compliance} & \textbf{Explanation} & \textbf{Key Strengths} \\
\hline

1 & firm_1.pdf & 0.122 & 83 & Simulated evaluation for applicant 2. The proposal shows good alignment with requirements. & Applicant 2 demonstrates strong capabilities in relevant areas. \\
\hline

2 & tender.pdf & 1.000 & 79 & Simulated evaluation for applicant 1. The proposal shows good alignment with requirements. & Applicant 1 demonstrates strong capabilities in relevant areas. \\
\hline

\end{longtable}

\section*{Detailed Applicant Analysis}


\subsection*{Rank 1: firm_1.pdf (Score: 83)}

\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{Metric} & \textbf{Value} \\
\hline
Compliance Score & 83/100 \\
Similarity Score & 0.122 \\
\hline
\end{tabularx}
\end{table}

\textbf{Explanation:} Simulated evaluation for applicant 2. The proposal shows good alignment with requirements.

\textbf{Strengths:} Applicant 2 demonstrates strong capabilities in relevant areas.

\textbf{Areas for Improvement:} Suggestions for improvement include more detailed technical specifications.

\textbf{Proposal Excerpt:} FIRM 1 PROPOSAL
Company: Tech Solutions Inc.
Experience: 7 years in software development
License: Valid business license #12345
Technical Specs: Full compliance with requirements
Timeline: 6 months with monthly milestones
Financial: $2M annual revenue, stable
Testing: Comprehensive QA procedures
Support: 24/7 technical support available
Scalability: Cloud-based scalable solution
Cost: $150,000 with payment terms
Standards: ISO 9001 certified

\newpage

\subsection*{Rank 2: tender.pdf (Score: 79)}

\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{Metric} & \textbf{Value} \\
\hline
Compliance Score & 79/100 \\
Similarity Score & 1.000 \\
\hline
\end{tabularx}
\end{table}

\textbf{Explanation:} Simulated evaluation for applicant 1. The proposal shows good alignment with requirements.

\textbf{Strengths:} Applicant 1 demonstrates strong capabilities in relevant areas.

\textbf{Areas for Improvement:} Suggestions for improvement include more detailed technical specifications.

\textbf{Proposal Excerpt:} TENDER DOCUMENT
Project: Software Development Services
Requirements:
1. Minimum 5 years experience
2. Valid business license
3. Technical specifications compliance
4. Project timeline and milestones
5. Financial stability demonstration

\newpage


\section*{Recommendations}

Based on the evaluation results, the following recommendations are provided:

\begin{enumerate}
    \item \textbf{Top-Ranked Applicant:} The applicant with the highest compliance score (firm_1.pdf) should be considered for further review.
    \item \textbf{Compliance Threshold:} Only applicants scoring above the minimum threshold should be considered for contract award.
    \item \textbf{Further Due Diligence:} Conduct additional verification for the top-ranked applicants before final selection.
\end{enumerate}

\section*{Methodology}

The evaluation process followed these steps:

\begin{enumerate}
    \item \textbf{Document Processing:} Text extraction from PDF documents using OCR when necessary.
    \item \textbf{Embedding Generation:} Creation of vector representations using nomic-embed-text model.
    \item \textbf{Similarity Search:} Semantic matching between requirements and proposals.
    \item \textbf{Rule-Based Filtering:} Application of budget, timeline, and certification constraints.
    \item \textbf{LLM Evaluation:} Detailed scoring and analysis using llama3.1 model.
\end{enumerate}

\end{document}